Kolmogorov-Smirnov

### 2020-04-09 ks/ks.Rmd
Spell check
Render KS to supmat

@@

@@

```{r}
knitr::kable(df_wide, caption = "Percentage of epitopes overlapping with transmembrane helix")
```

@@

```{r}
alpha <- 0.05
if (t$p.value <= alpha) {
  print("Reject that the two samples are taken from a same distribution") 
} else {
  print("Accept that the two samples are taken from a same distribution")
}
```

Plot:

>>>>

```{r}
alpha <- 0.05
if (t$p.value <= alpha) {
  verdict <- "Reject that the two samples are taken from a same distribution"
} else {
  verdict <- "Accept that the two samples are taken from a same distribution"
}
print(verdict)
```

@@

## Stats output

```{r}
names(t)
df_t_wide <- data.frame(
  statistic = t$statistic,
  p_value = t$p.value,
  alternative = t$alternative,
  method = t$method,
  data_name = t$data.name,
  alpha = alpha,
  verdict = verdict
)
df_t <- t(df_t_wide)
values <- df_t[,1]
param_names <- rownames(df_t)
df_t <- data.frame(
  parameter = param_names,
  value = values
)

knitr::kable(df_t, row.names = FALSE)
```

```{r}
write.csv(df_t, "ks.csv", row.names = FALSE)
```

## Plot

## Table

@@

```{r}
knitr::kable(df_wide, caption = "Percentage of MHC-I epitopes overlapping with transmembrane helix")
```

@@
